Revisiting the impact of deepfake technology towards viewer's political choice: A replication of Soubhik Barari (2021)

### 2021-03-22 outputs/paper/paper.Rmd
update result

## Regression diagnostics
Before conducting a linear regression, the following assumptions on data need to be checked :
whether there exists a linear relationship between independent variables and the target variable; 
whether residuals are independently normally distributed; 
if residuals have constant variance (homoscedasticity).
^[Regression diagnostics plots (Figure \@ref(fig:diagnostic)) can be created using the autoplot function in the “ggfortify” package @tang2016ggfortify] The results are shown in the graph below (Figure \@ref(fig:diagnostic)).
```{r model, echo=FALSE, warning=FALSE, fig.width=10, fig.height=4,message=FALSE}

## transfer data into dummy
#  select(-c(4))#  change categorical var to factors 
##create model

@@

```{r model_improved, echo=FALSE, warning=FALSE, fig.width=10, fig.height=2}
#model2 <- lm(sqrt(post_favor_Warren)~., data = FS)
#autoplot(model2,3)
```
**Residual and fitted plot: **
This plot  is used to check the linear relationship assumptions. A horizontal line, without distinct patterns is an indication for a linear relationship. Here we see that linearity seems to hold reasonably well, as the red line is close to the horizontal level (at 0). This suggests that we can assume a linear relationship between the predictors and the outcome variables [@bruce2020practical].

@@

```{r ttest1, echo=FALSE, fig.width=10, fig.height=3}
t1<-t.test(na.omit(dat$believed_true[dat$treat_fake_video == 1]), 
       na.omit(dat$believed_true[dat$treat_fake_audio == 1]))
m1<-tidy(t1, digits=1)
m1 %>%
  select(-c(estimate,statistic,parameter))%>%
 # rename(
   # AVG_deception_video=estimate1,
   # AVG_deception_audio=estimate2
 # )%>%
  kableExtra::kbl(caption="T test: Deception level of video vs audio")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

@@

m2 %>%
  select(-c(estimate,statistic,parameter))%>%
 # rename(
   # AVG_deception_video=estimate1,
   # AVG_deception_audio=estimate2
 # )%>%
  kableExtra::kbl(caption="T test: Deception level of video vs text")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

@@

m3 %>%
  select(-c(estimate,statistic,parameter))%>%
 # rename(
   # AVG_deception_video=estimate1,
   # AVG_deception_audio=estimate2
 # )%>%
  kableExtra::kbl(caption="T test: Deception level of video vs skit")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

@@

m1_a%>%
  select(-c(estimate,statistic,parameter))%>%
 # rename(
   # AVG_deception_video=estimate1,
   # AVG_deception_audio=estimate2
 # )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs control")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

Similarly, the same analysis has been done for the rest unpaired two-sample t-tests. In our study, we used a 5% significance level. Table \@ref(tab:attest2) shows the test result of how deepfake videos and texts impact audiences' feelings. The result shows that the difference in affect level between video (Mean = 41.28) and text (Mean=44.22) was not significant given the p-value is greater than 0.05.

@@

m2_a%>%
  select(-c(estimate,statistic,parameter))%>%
 # rename(
   # AVG_deception_video=estimate1,
   # AVG_deception_audio=estimate2
 # )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs text")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

Table \@ref(tab:attest3) shows the test result of how deepfake videos and audios impact audiences' feelings. The difference in affect level between video(Mean = 41.28) and audio (Mean=43.93) was not significant given the p-value is greater than 0.05.

@@

m3_a%>%
  select(-c(estimate,statistic,parameter))%>%
 # rename(
   # AVG_deception_video=estimate1,
   # AVG_deception_audio=estimate2
 # )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs audio")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

Table \@ref(tab:attest4) shows the test result of how deepfake videos and skit impact audiences feeling. The difference in affect level between video(Mean = 41.28) and skit (Mean=43) was not significant given the p-value is greater than 0.05.

@@

m4_a%>%
  select(-c(estimate,statistic,parameter))%>%
 # rename(
   # AVG_deception_video=estimate1,
   # AVG_deception_audio=estimate2
 # )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs skit")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

>>>>

## Regression diagnostics
Before conducting a linear regression, the following assumptions on data need to be checked :
whether there exists a linear relationship between independent variables and the target variable; 
whether residuals are independently normally distributed; 
if residuals have constant variance (homoscedasticity).
^[Regression diagnostics plots (Figure \@ref(fig:diagnostic)) can be created using the autoplot function in the “ggfortify” package @tang2016ggfortify] The results are shown in the graph below (Figure \@ref(fig:diagnostic)).
```{r model, echo=FALSE, warning=FALSE, fig.width=10, fig.height=4,message=FALSE}
##create model

@@

**Residual and fitted plot: **
This plot  is used to check the linear relationship assumptions. A horizontal line, without distinct patterns is an indication for a linear relationship. Here we see that linearity seems to hold reasonably well, as the red line is close to the horizontal level (at 0). This suggests that we can assume a linear relationship between the predictors and the outcome variables [@bruce2020practical].

@@

```{r ttest1, echo=FALSE, fig.width=10, fig.height=3}
t1<-t.test(na.omit(dat$believed_true[dat$treat_fake_video == 1]), 
       na.omit(dat$believed_true[dat$treat_fake_audio == 1]))
m1<-tidy(t1, digits=1)
m1 %>%
  select(-c(estimate,statistic,parameter))%>%
  mutate_if(is.numeric, format, digits=3)%>%  #change significant figure
  kableExtra::kbl(caption="T test: Deception level of video vs audio")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

@@

m2 %>%
  select(-c(estimate,statistic,parameter))%>%
  mutate_if(is.numeric, format, digits=3)%>%
  kableExtra::kbl(caption="T test: Deception level of video vs text")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

@@

m3 %>%
  select(-c(estimate,statistic,parameter))%>%
  mutate_if(is.numeric, format, digits=3)%>%
  kableExtra::kbl(caption="T test: Deception level of video vs skit")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

@@

m1_a%>%
  select(-c(estimate,statistic,parameter))%>%
  mutate_if(is.numeric, format, digits=3)%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs control")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

Similarly, the same analysis has been done for the rest unpaired two-sample t-tests. In our study, we used a 5% significance level. Table \@ref(tab:attest2) shows the test result of how deepfake videos and texts impact audiences' feelings. The result shows that the difference in affect level between video (Mean = 41.3) and text (Mean=44.2) was not significant given the p-value is greater than 0.05.

@@

m2_a%>%
  select(-c(estimate,statistic,parameter))%>%
  mutate_if(is.numeric, format, digits=3)%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs text")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

Table \@ref(tab:attest3) shows the test result of how deepfake videos and audios impact audiences' feelings. The difference in affect level between video(Mean = 41.3) and audio (Mean=43.9) was not significant given the p-value is greater than 0.05.

@@

m3_a%>%
  select(-c(estimate,statistic,parameter))%>%
  mutate_if(is.numeric, format, digits=3)%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs audio")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%   # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

Table \@ref(tab:attest4) shows the test result of how deepfake videos and skit impact audiences feeling. The difference in affect level between video(Mean = 41.3) and skit (Mean=43) was not significant given the p-value is greater than 0.05.

@@

m4_a%>%
  select(-c(estimate,statistic,parameter))%>%
  mutate_if(is.numeric, format, digits=3)%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs skit")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```
